PANCHANGE_analysis

### 2021-04-12 PANCHANGE_analysis.Rmd
changed forest plot legend for PCL to PCL-6

lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","PCL", "pcl.prepan.lm.for.plot")
lmoutput_format(pcl.retro.lm,"PCL.retrospective","PCL", "pcl.retro.lm.for.plot")

@@

# grouped by disorder measure
lmoutput_format_noexplan(gad.lm.noexplan,"GAD-7", "gad.lm.for.plot")
lmoutput_format_noexplan(phq.lm.noexplan,"PHQ-9", "phq.lm.for.plot")
lmoutput_format_noexplan(pcl.lm.noexplan,"PCL", "pcl.lm.for.plot")

@@

>>>>

lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","PCL-6", "pcl.prepan.lm.for.plot")
lmoutput_format(pcl.retro.lm,"PCL.retrospective","PCL-6", "pcl.retro.lm.for.plot")

@@

# grouped by disorder measure
lmoutput_format_noexplan(gad.lm.noexplan,"GAD-7", "gad.lm.for.plot")
lmoutput_format_noexplan(phq.lm.noexplan,"PHQ-9", "phq.lm.for.plot")
lmoutput_format_noexplan(pcl.lm.noexplan,"PCL-6", "pcl.lm.for.plot")

@@

plot.dat.disorder.retro <- plot.dat.disorder.retro %>%
  mutate(RowLabels = recode(RowLabels,
                            `PCL.retrospective` = "PCL total retrospective",
                            `PHQ.retrospective` = "PHQ total retrospective",
                            `GAD.retrospective` = "GAD total retrospective"))
